---
title: "Tutorial"
output: html_vignette
vignette: >
  %\VignetteIndexEntry{HW625 Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(HW625)
data(mtcars)
# For efficiency comparing
library(bench)
```


# Fit a linear model use mtcars data:
```{r}
# Fit a linear model
model <- lm(mpg ~ wt + hp + qsec + am, data = mtcars)

# Original `summary()` function
model_summary <- summary(model)
```


# Find SSE of the linear model:
```{r}
SSE <- obtain_SSE(model)
print(SSE)

# Compare the result with the original function
check_sse <- sum(model_summary$residuals ^ 2)
all.equal(check_sse, SSE)
```

Compare efficiency:
```{r}
results <- bench::mark(
  SSE,
  check_sse,
  check = FALSE
)
print(results)
```


# Find coefficients standard errors of the linear model:
```{r}
SE <- obtain_se(model)
print(SE)

# Compare the result with the original function
check_se <- model_summary$coefficients[, "Std. Error"]
all.equal(check_se, SE)
```

Compare efficiency:
```{r}
results <- bench::mark(
  SE,
  check_se,
  check = FALSE
)
print(results)
```


# Find t-statistic of the linear model:
```{r}
t_stats <- obtain_t_stats(model)
print(t_stats)

# Compare the result with the original function
check_t <- model_summary$coefficients[, "t value"]
all.equal(check_t, t_stats)
```

Compare efficiency:
```{r}
results <- bench::mark(
  t_stats,
  check_t,
  check = FALSE
)
print(results)
```


# Find p values of each t-statistic for the linear model:
```{r}
p_values <- obtain_p_value(model)
print(p_values)

# Compare the result with the original function
check_p <- model_summary$coefficients[, "Pr(>|t|)"]
all.equal(check_p, p_values)
```

Compare efficiency:
```{r}
results <- bench::mark(
  p_values,
  check_p,
  check = FALSE
)
print(results)
```


# Find residual standard error and degrees of freedom:
```{r}
resi_se <- obtain_residual_info(model)
print(resi_se)

# Compare the residual standard error with the original function
check_resi_se <- model_summary$sigma
all.equal(resi_se$residual_se, check_resi_se)

# Compare the degrees of freedom with the original function
check_resi_df <- model_summary$df[2]
all.equal(resi_se$df_resi, check_resi_df)
```

Compare efficiency:
```{r}
results1 <- bench::mark(
  resi_se$residual_se,
  check_resi_se,
  check = FALSE
)
print(results1)

results2 <- bench::mark(
  resi_se$df_resi,
  check_resi_df,
  check = FALSE
)
print(results2)
```


# Find R-square and adjusted R-square:
```{r}
R_sq <- obtain_r_square(model)
print(R_sq)

# Compare R-square with the original function
check_R_sq <- model_summary$r.squared
all.equal(R_sq$r_square, check_R_sq)

# Compare adjusted R-square with the original function
check_adj_R_sq <- model_summary$adj.r.squared
all.equal(R_sq$adj_r_square, check_adj_R_sq)
```

Compare efficiency:
```{r}
results1 <- bench::mark(
  R_sq$r_square,
  check_R_sq,
  check = FALSE
)
print(results1)

results2 <- bench::mark(
  R_sq$adj_r_square,
  check_adj_R_sq,
  check = FALSE
)
print(results2)
```


# Find F statistic, its p-value of the linear model, as well as the degrees of freedom for residuals and the model:
```{r}
f_stats <- obtain_f_stats(model)
print(f_stats)

# Compare F statistic with the original function
check_F <- model_summary$fstatistic[1]
all.equal(f_stats$f_statistic, check_F, check.attributes = FALSE)

# Compare numerator degrees of freedom with the original function
check_df <- model_summary$fstatistic[2]
all.equal(f_stats$df_model, check_df, check.attributes = FALSE)
```

Compare efficiency:
```{r}
results1 <- bench::mark(
  f_stats$f_statistic,
  check_F,
  check = FALSE
)
print(results1)

results2 <- bench::mark(
  f_stats$df_model,
  check_df,
  check = FALSE
)
print(results2)
```


# Obtain the summary for the linear model:
```{r}
# Apply lm_summary at confidence level 0.95
lm_summary(model)
```


Compare to `summary()`:
```{r}
model_summary
```


Compare efficiency:
```{r}
results <- bench::mark(
  lm_summary(model),
  model_summary,
  check = FALSE
)
print(results)
```
